An Open Platform for Managing Short Programming Exercises

### 2013-06-24 paper/paper.tex
avoid split infinitive

To date, each institution that has adopted CloudCoder in production has
provided Linux servers that we configured for them.  This has made
adoption very easy, but is not a model that is likely to scale well
to larger numbers of institutions.  We recently received a grant
of credits for Amazon Web Services\cite{aws} from Amazon,
which we plan to use to directly host CloudCoder for interested
institutions.  We are also investigating easier ways for
users to self-host. One possibility is enabling CloudCoder to run on application
hosting services such as Google App Engine\cite{gae}.
%  We have asked Amazon for Amazon Web Services credits to
%provide CloudCoder ``in the cloud'' to adopting institutions, and we
%hope to add support for Google App Engine this summer.  Ease of
%adoption is critical for CloudCoder.

>>>>

To date, each institution that has adopted CloudCoder in production has
provided Linux servers that we configured for them.  This has made
adoption very easy, but is not a model that is likely to scale well
to larger numbers of institutions.  We recently received a grant
of credits for Amazon Web Services\cite{aws} from Amazon,
which we plan to use to host CloudCoder directly for interested
institutions.  We are also investigating easier ways for
users to self-host. One possibility is enabling CloudCoder to run on application
hosting services such as Google App Engine\cite{gae}.
%  We have asked Amazon for Amazon Web Services credits to
%provide CloudCoder ``in the cloud'' to adopting institutions, and we
%hope to add support for Google App Engine this summer.  Ease of
%adoption is critical for CloudCoder.
